{\bf \Large The Power of Context in Decision-Making and Recommendations}

### 2023-08-03 darft_without_front_pages.tex
final version submission

\begin{dedication}

To my father, my first mentor, who seeded my enduring passion for learning.

\end{dedication}

@@

\section*{Acknowledgements}

Embarking on this scholarly journey has been both humbling and transformative, marked by countless days of meticulous study, intense deliberation, and profound discoveries. Indeed, the journey was punctuated with hurdles and moments of self-doubt. However, every trough was succeeded by a crest, each stumble by an ascent, and every challenge served as an opportunity. The path was steep, but it was these uphill struggles that honed my perspective, expanded my horizons, and ignited my passion for knowledge. The lessons learned, the triumphs celebrated, and the sense of accomplishment far outweighed the trials faced. Reflecting on these uplifting moments, I joyfully acknowledge those who accompanied me on this journey and made it not only possible but immensely rewarding.

Firstly, I extend my deepest gratitude to Zakaria Babutsidze, my PhD supervisor. He has been a great mentor and a source of inspiration for me. His honesty and straightforwardness challenged me to think critically and creatively, shaping me into someone better day by day. I am indebted to Francesco Castellanetta, our PhD program director, for his guiding hand and unwavering faith in my capabilities. I appreciate our long and intriguing discussions with Ludovic Diabaggio that transcended academia. I am grateful to William Rand for his invaluable insights and co-authorship. Daniela Iubatti, your informal talks and unwavering support have been a source of inspiration. I appreciate Diego Zunino for his earnest and invaluable guidance. Bruno Cirillo deserves special mention; our albeit slightly formal discussions have significantly shaped my work. My heartfelt appreciation goes to Renata Kaminska. Her support and intuitive understanding of my thoughts were indispensable in my pursuits. I am grateful to Benjamin Montmartin; our separate exchanges about wine (we were in France in the end) and statistics enriched my perspectives immeasurably. To Valerio Incerti, our creative discourses, even about less creative ideas were a constant source of inspiration. Lapo Mola’s precious feedback motivated me to pursue excellence, and I value that wholeheartedly.

Aytan, my beloved wife and best friend, your unwavering support and guidance have been my Polaris guiding me through the darkest nights and taught me to only settle for infinity and beyond. Ecem Delicik, my dear friend, I am grateful for the shared stories, moments, laughter, and silence that have strengthened our friendship. The moment you realized I was speaking to you in Turkish is unforgettable (I am sure, you still remember it too). Johanna Deperi, our shared moments and long talks were invaluable for self-reflection, joy, and sometimes, ``justified sadness'' throughout this journey. Artyom Yepremyan, our discussions helped us conquer the PhD mountain. I will forever cherish the times when I needed a hand, and you extended yours. Manon Desjardins, your constant support despite the towering stack of papers on your desk will always be appreciated. Mehdi Ibrahim, I am grateful for our coffee talks and the irresistible desserts from Morocco. Teymur Mardaliyev, your friendship and coding prowess have been invaluable; only you could convince me to settle for JavaScript there.

Finally, no amount of words can fully express my gratitude to my parents. Dad, your inquisitive nature has been my guiding star, instilling in me the curiosity that set me on this scholarly path. Your enthusiasm for the uncharted has been infectious, leading me to question, explore, and discover. Mom, you have been my anchor, reminding me of my roots and my identity amidst the academic whirlwind. Your unwavering encouragement and steadfast belief have reinforced my sense of self, allowing me to face challenges with courage and resilience. You taught me to stay grounded and true to myself, no matter how far I travel in the pursuit of knowledge. Your lessons continue to shape my journey, helping me navigate both personal and academic hurdles with grace and fortitude.

\textit{Çox sağ olun ki, varsınız!}

\clearpage
\tableofcontents
\newpage
\listoffigures
\clearpage
\listoftables
\newpage

\newpage
\section{Introduction}

>>>>

@@

\section{Introduction}
